---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 6,
  fig.retina = 3,
  out.width = "100%"
)
```

# ggsegBuckner

> **Work in Progress** — This package is under active development and has not yet been officially released.

Buckner cerebellar functional parcellation for the ggseg ecosystem.

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("ggseg/ggsegBuckner")
```

## 7-network parcellation
```{r "buckner7"}
library(ggseg)
library(ggsegBuckner)
library(ggplot2)

ggplot() +
  geom_brain(
    atlas = buckner7,
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = buckner7$palette, na.value = "grey") +
  theme_void() +
  ggtitle("Buckner 7-network cerebellar parcellation")
```

## 17-network parcellation
```{r "buckner17"}
ggplot() +
  geom_brain(
    atlas = buckner17,
    mapping = aes(fill = label),
    position = position_brain(. ~ view),
    show.legend = FALSE
  ) +
  scale_fill_manual(values = buckner17$palette, na.value = "grey") +
  theme_void() +
  ggtitle("Buckner 17-network cerebellar parcellation")
```

## Reference

Buckner RL et al. (2011). The organization of the human cerebellum estimated
by intrinsic functional connectivity. *Journal of Neurophysiology*, 106(5),
2322-2345.

## Code of Conduct

Please note that the ggsegBuckner project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this
project, you agree to abide by its terms.
